Mean of normal distribution

### 2020-08-26 mean_null.Rmd
clean null

```{r functions}

# create data for each levels
set.seed(12345)
create_simdata <- function(nx = 2, nsim = 5){
  mean_dist <- (1:nsim) %>% 
  purrr::map(function(i){
    x =  rgamma(nx, 0.5, 3)
    #p = 1-(1/nx)
    #b = stats::qnorm(p, mean(x), sd(x))
    #a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
    #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
    max(x)
    #mean(x)
  })
}
```

@@

nlevels = seq(2, 10, 1)

@@

```{r tidy_data_frame}
# nx = 20
# nsim = 500
# sim_dist <- rep(distributional::dist_gamma(0.2, 1), length(nx))
# 
# simdata_format <- function(nx, sim_dist)
# {
#   tibble(nlevel = seq_len(nx), sim_dist)
# }
# 
# create_simdata <- function(.data, nsim = 500)
# {
# nx = nrow(.data)
# sim_value <- seq_len(nx) %>%
#   purrr::map(function(i){
#     disti = .data %>% magrittr::extract(i,2)
#    distributional::generate(disti$sim_dist, nsim)
#   }) %>% enframe()
# .data %>% bind_cols(sim_value)
# #data %>% mutate(sim_value = data)
# }
# 
# data <- simdata_format(nx, sim_dist) %>%
#   create_simdata()
# 
# data %>%
#   select(-sim_dist, -name) %>%
#   unnest(value) %>%
#   unnest(value) %>%
#   ggplot(aes(x = value)) +
#   geom_histogram() +
#   facet_wrap(~nlevel)

>>>>

```{r functions}
# create data for each levels
set.seed(12345)
create_simdata <- function(nx = 2, nsim = 5, sim_dist = distributional::dist_gamma(0.5, 3)){
  mean_dist <- (1:nsim) %>% 
  purrr::map(function(i){
    #x =  rgamma(nx, 0.5, 3)
    x =  sim_dist %>% distributional::generate(nx) %>% unlist()
    p = 1-(1/nx)
    b = stats::qnorm(p, mean(x), sd(x))
    a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
    k = stats::quantile(x, p, type = 8, na.rm = TRUE)
    (max(x)-a)/b
    # max(x)
  })
}
```

@@

nlevels = seq(60, 100, 5)

@@
